Tidy data structure to support exploration and modeling of temporal data

### 2018-12-02 main.Rmd
added Modularity

Time representation could be arbitrary, for example R's native `POSIXct` and `Date` for versatile date-times, nano time for nanosecond resolution [@R-nanotime], and pure numbers in simulations. Yet ordered factors can also be a source of time, such as month names from January to December and weekdays from Monday to Sunday. New index classes are introduced to accurately represent year-week, year-month and year-quarter. Supporting a wide array of time types is a must for a tsibble, and extending for new types is a plus.

@@

The **tsibble** package highly features modularity and extensibility.

@@

@@

As a fundamental infrastructure, extensibility is highly valued and one of the core design features in the **tsibble** package. Contrary to the "data first" principle for end users, extensibility is developer focused and would be mostly used in dependent packages, which heavily relies on S3 classes and methods in R [@adv-r]. It can be extended in two major aspects: custom index and new tsibble class.

Tsibble supports an extensive range of index types from numerics to nano time, but there might be custom indices used for some occasions, for example school semesters. These academic terms vary from one institute to another within an academic year, which is defined differently from a calendar year. New index would be immediately recognized by the software once `index_valid()` defined, as long as it can be ordered from past to future. The interval regarding semesters is further outlined through `pull_interval()`. As a result, the rest software methods such as `has_gaps()`, `count_gaps()` and `fill_gaps()` will have instant support for data that contains this new index.

>>>>

@@

data-centric & human-centered.

@@

Modular programming is adopted while designing the **tsibble** package. Modularity benefits users with variety and flexibility and developers with easy maintenance.

All user-facing functions can be roughly organized into three major chunks according to their functionality: vector functions (1d), table verbs (2d), and window family. Each chunk is an independent module, but works interdependently. Vector functions in the package mostly deal with time. When collapsing a tsibble to less granular interval, these atomic functions can be combined with the `index_by()` table verb to accomplish this. A different function results in easily switching to aggregation of different time resolution. Since these functions are not exclusive to a tsibble, they can be used in a variety of applications in conjunction with other packages. On the other hand, these tsibble verbs can incorporate many third-party vector functions to step out of current tsibble zone. It is generally easier to trace back the errors users encounter from separating 1d and 2d functions.

@@

As a fundamental infrastructure, extensibility is a design decision that is focused on from the start of **tsibble**'s development. Contrary to the "data first" principle for end users, extensibility is developer focused and would be mostly used in dependent packages, which heavily relies on S3 classes and methods in R [@adv-r]. It can be extended in two major aspects: custom index and new tsibble class.

Time representation could be arbitrary, for example R's native `POSIXct` and `Date` for versatile date-times, nano time for nanosecond resolution [@R-nanotime], and pure numbers in simulations. Yet ordered factors can also be a source of time, such as month names from January to December and weekdays from Monday to Sunday. Tsibble supports an extensive range of index types from numerics to nano time, but there might be custom indices used for some occasions, for example school semesters. These academic terms vary from one institute to another within an academic year, which is defined differently from a calendar year. New index would be immediately recognized by the software once `index_valid()` defined, as long as it can be ordered from past to future. The interval regarding semesters is further outlined through `pull_interval()`. As a result, the rest software methods such as `has_gaps()`, `count_gaps()` and `fill_gaps()` will have instant support for data that contains this new index.
